E4-analysis-comparison-to-original

### 2022-04-01 group-d/E4-analysis-ROIs.Rmd
added calibration, comparison to original, and ROI analysis for E4 to manuscript

```{r , include=FALSE}
library(papaja)
library(jsonlite)
library(tidyverse)
library(lmerTest)
library(afex)
library(forcats)
library(broom.mixed)
```

@@

padding = -50
eyetracking.data.with.quadrant.roi <- eyetracking.data %>%
  left_join(screen.data, by = 'subject') %>% 
  #filter(!subject %in% bad.eyetracking.data.subjects) %>% 
  #filter(x >= 0, y >= 0) %>% # negative values indicate something's incorrect (drops about 12,000 rows!!)
  mutate(in.roi.0 = in.box(x,y, left = 0, right = screen_width/2, top = 0, bottom = screen_height/2, padding )) %>%
  mutate(in.roi.1 = in.box(x,y, left = screen_width/2, right = screen_width, top = 0, bottom = screen_height/2, padding )) %>%
  mutate(in.roi.2 = in.box(x,y, left = screen_width/2, right = screen_width, top = screen_height/2 , bottom = screen_height, padding )) %>%
  mutate(in.roi.3 = in.box(x,y, left = 0, right = screen_width/2, top = screen_height/2 , bottom = screen_height, padding )) %>% 
  mutate(in.roi.instrument = case_when(
    target_instrument == '#jspsych-free-sort-draggable-0' | target_instrument == '#jspsych-freesort-draggable-0'  ~ in.roi.0,
    target_instrument == '#jspsych-free-sort-draggable-1' | target_instrument == '#jspsych-freesort-draggable-1' ~ in.roi.1,
    target_instrument == '#jspsych-free-sort-draggable-2' | target_instrument == '#jspsych-freesort-draggable-2' ~ in.roi.2,
    target_instrument == '#jspsych-free-sort-draggable-3' | target_instrument == '#jspsych-freesort-draggable-3' ~ in.roi.3
  )) %>%
  mutate(in.roi.animal = case_when(
    target_animal == '#jspsych-free-sort-draggable-0' | target_animal == '#jspsych-freesort-draggable-0' ~ in.roi.0,
    target_animal == '#jspsych-free-sort-draggable-1' | target_animal == '#jspsych-freesort-draggable-1' ~ in.roi.1,
    target_animal == '#jspsych-free-sort-draggable-2' | target_animal == '#jspsych-freesort-draggable-2' ~ in.roi.2,
    target_animal == '#jspsych-free-sort-draggable-3' | target_animal == '#jspsych-freesort-draggable-3' ~ in.roi.3
  )) %>% 
  #sample_n(100) %>% 
  rowwise() %>% 
  mutate(roi_vec = list(c(in.roi.0, in.roi.1, in.roi.2, in.roi.3)),
         which_roi = ifelse(sum(roi_vec)==1, which(unlist(roi_vec) == TRUE), 99 ) ) 
```

```{r}

@@

```{r}

ggplot(eyetracking.data.with.roi %>% filter(subject == '5564e577fdf99b6c901a75a6'))+
  geom_point(aes(x = x, y = y, color = as.factor(which_roi)))+
  scale_y_reverse()
```

```{r}

ggplot(eyetracking.data.with.quadrant.roi %>% filter(subject == '5564e577fdf99b6c901a75a6'))+
  geom_point(aes(x = x, y = y, color = as.factor(which_roi)))+
  scale_y_reverse()
```
```{r}

@@

```{r E4-average-onsets-of-critical-words-ROIs}
#Calculate average animal onset
animal.onset <- audio.info %>% pull(onset_noun) %>% mean()
instrument.onset <- audio.info %>% pull(onset_instrument) %>% mean()
```

@@

```{r}

ggplot(eyetracking.data.with.time.windows.quadrant %>%filter(subject %in% calib.by.subj[calib.by.subj$mean_percent_in_roi>75,]$subject) %>%
         filter(in.roi.animal)) +
                # calib_by_subj comes from the calibration analysis rmd          
  geom_vline(aes(xintercept=screen_width/2))+
  geom_hline(aes(yintercept=screen_height/2))+
  geom_point(aes(x = x, y = y), alpha=0.2)+
  facet_grid(time.window~target_animal)+
  scale_y_reverse()
```

@@

```{r E4-summarizing-gaze-data-for-plotting-ROIs}
#Summarize data for plotting
eyetracking.figure.2.data <- eyetracking.data.with.time.windows %>%
               filter(subject %in% calib.by.subj[calib.by.subj$mean_percent_in_roi>50,]$subject) %>% # calib_by_subj comes from the calibration analysis rmd %>%
  filter(between(t.window , -200, 4000)) %>%
  group_by(subject, compatibility, t.window) %>%
  summarize(p.animal = mean(in.roi.animal), p.instrument = mean(in.roi.instrument)) %>%
  pivot_longer(c('p.animal', 'p.instrument'), names_to="object_type", values_to="prop_fixations") %>%
  #mutate(prop_fixations = if_else(is.na(prop_fixations), 0, prop_fixations)) %>%
  group_by(compatibility, t.window, object_type) %>%
  summarize(M=mean(prop_fixations), SE=sd(prop_fixations)/sqrt(n()))
```

```{r E4-gaze-timecourse-fig-ROIs, fig.cap = "Timecourse of eye-gaze to target animal and target instrument by verb bias condition. Vertical lines indicate average onsets of animal and instrument offset by 200ms."}

@@

```{r E4-summarizing-gaze-data-for-plotting-quadrants}
#Summarize data for plotting
eyetracking.figure.3.data <- eyetracking.data.with.time.windows.quadrant %>%
               filter(subject %in% calib.by.subj[calib.by.subj$mean_percent_in_roi>50,]$subject) %>% # calib_by_subj comes from the calibration analysis rmd
  filter(between(t.window , -200, 4000)) %>%
  group_by(subject, compatibility, t.window) %>%
  summarize(p.animal = mean(in.roi.animal), p.instrument = mean(in.roi.instrument)) %>%
  pivot_longer(c('p.animal', 'p.instrument'), names_to="object_type", values_to="prop_fixations") %>%
  #mutate(prop_fixations = if_else(is.na(prop_fixations), 0, prop_fixations)) %>%
  group_by(compatibility, t.window, object_type) %>%
  summarize(M=mean(prop_fixations), SE=sd(prop_fixations)/sqrt(n()))
```

```{r E4-gaze-timecourse-fig-ROIs, fig.cap = "Timecourse of eye-gaze to target animal and target instrument by verb bias condition. Vertical lines indicate average onsets of animal and instrument offset by 200ms."}

@@

```{r }
data.time.window.1 <- eyetracking.window.summary.by.trial %>% filter(time.window == "post-verb-onset-pre-animal-onset")

model.time.window.1 <- lmer(prop.fixations.animal ~ compatibility + (1  | subject) + (1 | trialID), data=data.time.window.1,
                            control = lmerControl(optimizer = "bobyqa",
                                                  optCtrl = list(maxfun = 2e6)))

summary(model.time.window.1)
```

```{r }
data.time.window.2 <- eyetracking.window.summary.by.trial %>% filter(time.window == "post-animal-onset-pre-instrument-onset")

model.time.window.2 <- lmer(prop.fixations.animal ~ compatibility + (1  | subject) + (1 | trialID), data=data.time.window.2)

summary(model.time.window.2)
```

@@

summary(model.time.window.3)
```

```{r E4-ET-analysis-tables}
E4_ET_model1_tab = broom.mixed::tidy(model.time.window.1) 
E4_ET_model2_tab = broom.mixed::tidy(model.time.window.2) 
E4_ET_model3_tab = broom.mixed::tidy(model.time.window.3)

E4_ET_model1_c1 = E4_ET_model1_tab %>% filter(term == "compatibility1")
E4_ET_model1_c2 = E4_ET_model1_tab %>% filter(term == "compatibility2")

E4_ET_model2_c1 = E4_ET_model2_tab %>% filter(term == "compatibility1")
E4_ET_model2_c2 = E4_ET_model2_tab %>% filter(term == "compatibility2")

@@

>>>>

```{r , include=FALSE}
library(papaja)
library(jsonlite)
library(tidyverse)
library(lmerTest)
library(afex)
library(forcats)
library(broom.mixed)
library(patchwork)
```

@@

padding = 0
eyetracking.data.with.quadrant.roi <- eyetracking.data %>%
  left_join(screen.data, by = 'subject') %>% 
  #filter(!subject %in% bad.eyetracking.data.subjects) %>% 
  #filter(x >= 0, y >= 0) %>% # negative values indicate something's incorrect (drops about 12,000 rows!!)
  mutate(in.roi.0 = in.box(x,y, left = 0, right = screen_width/2, top = 0, bottom = screen_height/2, padding )) %>%
  mutate(in.roi.1 = in.box(x,y, left = screen_width/2, right = screen_width, top = 0, bottom = screen_height/2, padding )) %>%
  mutate(in.roi.2 = in.box(x,y, left = screen_width/2, right = screen_width, top = screen_height/2 , bottom = screen_height, padding )) %>%
  mutate(in.roi.3 = in.box(x,y, left = 0, right = screen_width/2, top = screen_height/2 , bottom = screen_height, padding )) %>% 
  mutate(in.roi.instrument = case_when(
    target_instrument == '#jspsych-free-sort-draggable-0' | target_instrument == '#jspsych-freesort-draggable-0'  ~ in.roi.0,
    target_instrument == '#jspsych-free-sort-draggable-1' | target_instrument == '#jspsych-freesort-draggable-1' ~ in.roi.1,
    target_instrument == '#jspsych-free-sort-draggable-2' | target_instrument == '#jspsych-freesort-draggable-2' ~ in.roi.2,
    target_instrument == '#jspsych-free-sort-draggable-3' | target_instrument == '#jspsych-freesort-draggable-3' ~ in.roi.3
  )) %>%
  mutate(in.roi.animal = case_when(
    target_animal == '#jspsych-free-sort-draggable-0' | target_animal == '#jspsych-freesort-draggable-0' ~ in.roi.0,
    target_animal == '#jspsych-free-sort-draggable-1' | target_animal == '#jspsych-freesort-draggable-1' ~ in.roi.1,
    target_animal == '#jspsych-free-sort-draggable-2' | target_animal == '#jspsych-freesort-draggable-2' ~ in.roi.2,
    target_animal == '#jspsych-free-sort-draggable-3' | target_animal == '#jspsych-freesort-draggable-3' ~ in.roi.3
  )) %>% 
  #sample_n(100) %>% 
  rowwise() %>% 
  mutate(roi_vec = list(c(in.roi.0, in.roi.1, in.roi.2, in.roi.3)),
         which_roi = ifelse(sum(roi_vec)==1, which(unlist(roi_vec) == TRUE), 99 ) ) 
```

```{r, eval = F}

@@

Eye-tracking on the web differs critically from in-lab eye-tracking in that the size of the display differs across participants. Thus the size of the ROIs differs across participants. The current version of the web experiment used a bounding box around each image to determine the ROI. 
This approach is flexible and accomodates variability in image size, but may exclude looks that are directed at the image but fall outside of the image (due to participant or eye-tracker noise) as show in Figure \@ref(fig:E4-example-subj-looks-ROI)a. Alternatively, The display can be split into 4 quadrants which jointly cover the entire screen (see Figure \@ref(fig:E4-example-subj-looks-ROI)b).

```{r E4-example-subj-looks-ROI, fig.cap = "Example participant's gaze coordinates categorized into ROIs based on a) image bounding boxes and b) screen quadrants. Magenta points indicate looks that were not categorized into an ROI"}
p_box<-ggplot(eyetracking.data.with.roi %>% filter(subject == '5564e577fdf99b6c901a75a6'))+
  geom_point(aes(x = x, y = y, color = as.factor(which_roi)))+
  scale_y_reverse()+
  theme_bw()+
  theme(legend.position = "none")
p_quad<-ggplot(eyetracking.data.with.quadrant.roi %>% filter(subject == '5564e577fdf99b6c901a75a6'))+
  geom_point(aes(x = x, y = y, color = as.factor(which_roi)))+
  scale_y_reverse()+ 
  theme_bw()+
  theme(legend.position = "none")

p_box + p_quad + plot_annotation(tag_levels = 'a')
```

```{r, eval = F}

@@

```{r }
#Calculate average animal onset
animal.onset <- audio.info %>% pull(onset_noun) %>% mean()
instrument.onset <- audio.info %>% pull(onset_instrument) %>% mean()
```

@@

```{r, eval = F}

ggplot(eyetracking.data.with.time.windows.quadrant %>%
         # filter(subject %in% calib.by.subj[calib.by.subj$mean_percent_in_roi>75,]$subject) %>%
         filter(in.roi.animal)) +
                # calib_by_subj comes from the calibration analysis rmd          
  geom_vline(aes(xintercept=screen_width/2))+
  geom_hline(aes(yintercept=screen_height/2))+
  geom_point(aes(x = x, y = y), alpha=0.2)+
  facet_grid(time.window~target_animal)+
  scale_y_reverse()
```

@@

```{r E4-summarizing-gaze-data-for-plotting-ROIs}
#Summarize data for plotting
eyetracking.figure.2.data <- eyetracking.data.with.time.windows %>%
              # filter(subject %in% calib.by.subj[calib.by.subj$mean_percent_in_roi>50,]$subject) %>% # calib_by_subj comes from the calibration analysis rmd %>%
  filter(between(t.window , -200, 4000)) %>%
  group_by(subject, compatibility, t.window) %>%
  summarize(p.animal = mean(in.roi.animal), p.instrument = mean(in.roi.instrument)) %>%
  pivot_longer(c('p.animal', 'p.instrument'), names_to="object_type", values_to="prop_fixations") %>%
  #mutate(prop_fixations = if_else(is.na(prop_fixations), 0, prop_fixations)) %>%
  group_by(compatibility, t.window, object_type) %>%
  summarize(M=mean(prop_fixations), SE=sd(prop_fixations)/sqrt(n()))
```

```{r , eval = F}

@@

```{r E4-summarizing-gaze-data-for-plotting-quadrants}
#Summarize data for plotting
eyetracking.figure.3.data <- eyetracking.data.with.time.windows.quadrant %>%
             #  filter(subject %in% calib.by.subj[calib.by.subj$mean_percent_in_roi>50,]$subject) %>% # calib_by_subj comes from the calibration analysis rmd
  filter(between(t.window , -200, 4000)) %>%
  group_by(subject, compatibility, t.window) %>%
  summarize(p.animal = mean(in.roi.animal), p.instrument = mean(in.roi.instrument)) %>%
  pivot_longer(c('p.animal', 'p.instrument'), names_to="object_type", values_to="prop_fixations") %>%
  #mutate(prop_fixations = if_else(is.na(prop_fixations), 0, prop_fixations)) %>%
  group_by(compatibility, t.window, object_type) %>%
  summarize(M=mean(prop_fixations), SE=sd(prop_fixations)/sqrt(n()))
```

```{r E4-gaze-timecourse-fig-quadrants, fig.cap = "Timecourse of eye-gaze to target animal and target instrument by verb bias condition with gaze categorized based on which quadrant of the screen the coordinates fall in (as opposed to a bounding box around the image). Vertical lines indicate average onsets of animal and instrument offset by 200ms."}

@@

@@

#summary(model.time.window.3)
```

```{r }
#E4_ET_model1_tab = broom.mixed::tidy(model.time.window.1) 
#E4_ET_model2_tab = broom.mixed::tidy(model.time.window.2) 
E4_ET_model3_tab = broom.mixed::tidy(model.time.window.3)

@@

Categorizing gaze location based on which of the four quadrants of the screen the coordinates fell in, increases the overall proportions of fixations (see Figure \@ref(fig:E4-gaze-timecourse-fig-quadrants)).  In the _post-instrument_ window, participants looked more at the target animal in the modifier-biased condition and the equi-biased conditions relative to the instrument-biased condition ( _b_ =  `r E4_ET_model3_c1 %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r E4_ET_model3_c1 %>% pull(std.error) %>% round(digits = 2)`, _p_ <  0.01) and marginally so in the modifier biased condition relative to the equi-biased condition ( _b_ =  `r E4_ET_model3_c2 %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r E4_ET_model3_c2 %>% pull(std.error) %>% round(digits = 2)`, _p_ =  `r E4_ET_model3_c2 %>% pull(p.value) %>% round(digits = 2)`). Effect size estimates appeared somewhat larger and noise was somewhat reduced when using the quadrant categorization relative to the bounding box-based ROIs.

### 2022-04-01 group-d/E4-analysis-calibration.Rmd
added calibration, comparison to original, and ROI analysis for E4 to manuscript

```{r}
ggplot(summary.data.calib)+
  geom_line(aes(x = calib_num, y = mean_percent_in_roi, color=subject))+
  theme_bw()+
  theme(legend.position = "none") 
```
```{r}
summary.data.calib.wide = summary.data.calib %>% 
  select(-trial_index) %>% 
  pivot_wider(id_cols = subject, names_from=calib_num, values_from = mean_percent_in_roi )

@@

eyetracking.effects.by.subj = read_csv( "output/E4_eye-tracking_data.csv") %>% 
  rename("condition" = compatibility) %>% 
  filter(time.window == "post-instrument-onset", condition != "filler" ) %>% 
  group_by(condition, time.window, subject) %>% 
  summarize(M = mean(prop.fixations.animal)) %>% 
  pivot_wider(names_from = condition, values_from = M) %>% 
  mutate(bias_effect = modifier - instrument) %>% 
  left_join(calib.by.subj, by = "subject")
```

```{r}
ggplot(eyetracking.effects.by.subj, aes(x = mean_percent_in_roi, y = modifier))+
  geom_point()+
  geom_smooth(method = "lm")
```

```{r}
ggplot(eyetracking.effects.by.subj, aes(x = mean_percent_in_roi, y = bias_effect))+
  geom_point()+
  geom_smooth(method = "lm")
```
```{r}
eyetracking.window.3 = read_csv( "output/E4_eye-tracking_data.csv") %>% 
  filter(time.window == "post-instrument-onset", compatibility != "filler" ) %>% 
  mutate(condition = factor(compatibility, levels = c('instrument', 'equibiased', 'modifier'))) %>% 
  left_join(calib.by.subj, by = "subject")
```

@@

model.time.window.3 <- lmer(prop.fixations.animal ~ condition + (1  | subject) + (1 | trialID), data=eyetracking.window.3,
                            control = lmerControl(optimizer = "bobyqa",
                                                  optCtrl = list(maxfun = 2e6)))
summary(model.time.window.3)
```

@@

model.time.window.3.good.calib <- lmer(prop.fixations.animal ~ condition + (1  | subject) + (1 | trialID), data=eyetracking.window.3.good.calib,
                            control = lmerControl(optimizer = "bobyqa",
                                                  optCtrl = list(maxfun = 2e6)))
summary(model.time.window.3.good.calib)
```

@@

model.time.window.3.great.calib <- lmer(prop.fixations.animal ~ condition + (1  | subject) + (1 | trialID), data=eyetracking.window.3.great.calib,
                            control = lmerControl(optimizer = "bobyqa",
                                                  optCtrl = list(maxfun = 2e6)))
summary(model.time.window.3.great.calib)
```

>>>>

```{r, eval = F}
ggplot(summary.data.calib)+
  geom_line(aes(x = calib_num, y = mean_percent_in_roi, color=subject))+
  theme_bw()+
  theme(legend.position = "none") 
```
```{r, eval=F}
summary.data.calib.wide = summary.data.calib %>% 
  select(-trial_index) %>% 
  pivot_wider(id_cols = subject, names_from=calib_num, values_from = mean_percent_in_roi )

@@

eyetracking.effects.by.subj = read_csv( "output/E4_eye-tracking_data.csv") %>% 
  rename("condition" = compatibility) %>% 
  filter(time.window == "post-instrument-onset", condition != "filler" ) %>% 
  group_by(condition, time.window, subject) %>% 
  summarize(M = mean(prop.fixations.animal)) %>% 
  pivot_wider(names_from = condition, values_from = M) %>% 
  mutate(bias_effect = modifier - instrument) %>% 
  left_join(calib.by.subj, by = "subject")

```
```{r, eval = F}
ggplot(eyetracking.effects.by.subj, aes(x = mean_percent_in_roi, y = modifier))+
  geom_point()+
  geom_smooth(method = "lm")
```

```{r,eval=F}
write_csv(calib.by.subj,"output/calib_by_subj.csv")
```

m_calib = broom::tidy(lm(bias_effect ~ mean_percent_in_roi, data = eyetracking.effects.by.subj))
#m_calib 
```

```{r}
m_calib_b = m_calib %>% filter(term ==  'mean_percent_in_roi') %>% pull(estimate ) %>% round(digits = 3)
m_calib_se = m_calib %>% filter(term ==  'mean_percent_in_roi') %>% pull(std.error ) %>% round(digits = 3)
m_calib_p = m_calib %>% filter(term ==  'mean_percent_in_roi') %>% pull(p.value ) %>% round(digits = 3)
```

```{r, eval = F}
ggplot(eyetracking.effects.by.subj, aes(x = mean_percent_in_roi, y = bias_effect))+
  geom_point()+
  geom_smooth(method = "lm")
```
Participants' calibration quality, measured as the mean percentage of fixations that landed within XX pixels of the calibration point, varied substantially (`r range(calib.by.subj$mean_percent_in_roi) |> round(digits = 2)`). 
The quality of a participant's calibration significantly predicted the participant's effect size. 
The difference in target animal fixation proportions between modifier and instrument conditions was higher for participants with better calibration ($b=$`r m_calib_b`,$SE=$`r m_calib_se`, $p=$`r m_calib_p`).

```{r}
eyetracking.window.3 = read_csv( "output/E4_eye-tracking_data.csv") %>% 
  filter(time.window == "post-instrument-onset", compatibility != "filler" ) %>% 
  mutate(condition = factor(compatibility, levels = c('instrument', 'equibiased', 'modifier'))) %>% 
  left_join(calib.by.subj, by = "subject")
```

@@

```{r , eval = F}

model.time.window.3 <- lmer(prop.fixations.animal ~ condition + (1 +condition | subject) + (1 | trialID), data=eyetracking.window.3,
                            control = lmerControl(optimizer = "bobyqa",
                                                  optCtrl = list(maxfun = 2e6)))
summary(model.time.window.3)
```

@@

m.good.calib <- lmer(prop.fixations.animal ~ condition + (1  | subject) + (1 | trialID), data=eyetracking.window.3.good.calib,
                            control = lmerControl(optimizer = "bobyqa",
                                                  optCtrl = list(maxfun = 2e6)))
#summary(m.good.calib)

m_calib_good = broom.mixed::tidy(m.good.calib)

m_calib_good_c1 = m_calib_good %>% filter(term == "condition1")
m_calib_good_c2 = m_calib_good %>% filter(term == "condition2")

```

Replicating the linear mixed-effects analysis (in the post-instrument onset time window only) on a subset of 35 participants with calibration quality >50% suggests that the effect of verb bias condition was larger in this subset than in the full dataset. Participants looked more at the target animal in the modifier-biased condition and the equi-biased conditions relative to the instrument-biased condition ( _b_ =  `r m_calib_good_c1 %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r m_calib_good_c1 %>% pull(std.error) %>% round(digits = 2)`, _p_ <  0.001) but not significantly so in the modifier biased condition relative to the equi-biased condition ( _b_ =  `r m_calib_good_c2 %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r m_calib_good_c2 %>% pull(std.error) %>% round(digits = 2)`, _p_ =  `r m_calib_good_c2 %>% pull(p.value) %>% round(digits = 2)`).

@@

m.great.calib <- lmer(prop.fixations.animal ~ condition + (1  | subject) + (1 | trialID), data=eyetracking.window.3.great.calib,
                            control = lmerControl(optimizer = "bobyqa",
                                                  optCtrl = list(maxfun = 2e6)))
#summary(m.great.calib)
m_calib_great = broom.mixed::tidy(m.great.calib)

m_calib_great_c1 = m_calib_great %>% filter(term == "condition1")
m_calib_great_c2 = m_calib_great %>% filter(term == "condition2")
```

Replicating the linear mixed-effects analysis (in the post-instrument onset time window only) on a subset of 19 participants with calibration quality >75% suggests that the effect of verb bias condition was larger in this subset than in the full dataset. 
Participants looked more at the target animal in the modifier-biased condition and the equi-biased conditions relative to the instrument-biased condition ( _b_ =  `r m_calib_great_c1 %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r m_calib_great_c1 %>% pull(std.error) %>% round(digits = 2)`, _p_ <  0.001) but not significantly so in the modifier biased condition relative to the equi-biased condition ( _b_ =  `r m_calib_great_c2 %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r m_calib_great_c2 %>% pull(std.error) %>% round(digits = 2)`, _p_ =  `r m_calib_great_c2 %>% pull(p.value) %>% round(digits = 2)`).

### 2022-04-01 group-d/E4-analysis-comparison-to-original.Rmd
added calibration, comparison to original, and ROI analysis for E4 to manuscript

In addition to qualitatively replicating the action and eye-tracking results, the quantitative patterns were similar to those observed in the dataset which was the target of replication.

@@

@@

```{r}
eyetracking.window.summary.by.subj.both = bind_rows(eyetracking.window1.summary.by.trial.orig, eyetracking.window2.summary.by.trial.orig, eyetracking.window3.summary.by.trial.orig, eyetracking.window.summary.by.trial) %>% 
   filter(time.window != "end", time.window != "pre-verb-onset", condition != "filler" ) %>% 
  group_by(study, condition, time.window, subject) %>% 
  summarize(M = mean(prop.fixations.animal)) %>% 
  mutate(time.window = factor(time.window, 
                            levels = c("post-verb-onset-pre-animal-onset",
                                       "post-animal-onset-pre-instrument-onset",
                                       "post-instrument-onset")))
```

```{r E4-proportion-fix-by-window-both, fig.cap = "Proportion of target fixations by verb bias in the original dataset (Ryskin et al., 2017) and the current data collected online."}

ggplot(eyetracking.window.summary.by.subj.both)+
  stat_summary(aes(x=time.window, fill=condition, y = M, alpha = study), 
               geom = 'point', fun = 'mean', shape = 21, size = 3)+
  stat_summary(aes(x=as.numeric(time.window), fill=condition, y = M, linetype = study), geom = 'line', fun = 'mean', alpha = 0.5)+
  #facet_wrap(~time.window)+
  #geom_errorbar(position=position_dodge(width=0.9), width=0.2)+
  #scale_fill_brewer(palette = "Set1", name = "Location", labels = c("Animal", "Instrument", "Other"))+
  scale_alpha_manual(values = c(0.5,1))+
  scale_linetype_manual(values = c("dashed","solid"))+
  coord_cartesian(ylim = c(0,.8))+
  theme_classic()+
  labs(y = "Proportion of fixations", x = NULL)
```
Something funky going on with this graph...

```{r}
orig.data.time.window.1 <- eyetracking.window1.summary.by.trial.orig %>% 
  filter(condition != "filler") %>% 
  mutate(condition = fct_drop(condition))
contrasts(orig.data.time.window.1$condition) <- cbind(c(-2/3, 1/3, 1/3), c(0, -1/2, 1/2))

@@

```{r}
orig.data.time.window.2 <- eyetracking.window2.summary.by.trial.orig %>% 
  filter(condition != "filler") %>% 
  mutate(condition = fct_drop(condition))
contrasts(orig.data.time.window.2$condition) <- cbind(c(-2/3, 1/3, 1/3), c(0, -1/2, 1/2))

@@

```{r}
orig.data.time.window.3 <- eyetracking.window3.summary.by.trial.orig %>% 
  filter(condition != "filler") %>% 
  mutate(condition = fct_drop(condition))
contrasts(orig.data.time.window.3$condition) <- cbind(c(-2/3, 1/3, 1/3), c(0, -1/2, 1/2))

model.time.window.3 <- lmer(prop.fixations.animal ~ condition + (1 | subject) + (1 | trialID), data=orig.data.time.window.3 )
summary(model.time.window.3)
```
```

>>>>

The web version of the study qualitatively replicates the action and eye-tracking results of the original dataset [@ryskinVerbBiasesAre2017]. 
The mouse click results from both studies are summarized in Figure \@ref(fig:E4-mouse-moves-fig-web-and-orig).
The quantitative patterns of clicks were similar to those observed in the original dataset, though for Instrument-biased verbs, clicks were closer to evenly split between the animal and the instrument relative to the in-lab study where they were very clearly biased toward the instrument.

@@

The eye-tracking results from both studies are summarized in Figure \@ref(fig:E4-proportion-fix-by-window-both). 
For simplicity, and to reflect the dependent variable used in analyses, we average the proportion of fixations to the target animal within each time window.
Though the qualitative patterns are replicated, proportions of fixations to the target animal were much lower in the web version of the study. 
This may reflect the fact that participants in the web study are less attentive and/or the quality of the webgazer eye-tracking system is lower, relative to the Eyelink 1000 which was used for the original study.

@@

```{r}
eyetracking.window.summary.by.subj.both = bind_rows(eyetracking.window1.summary.by.trial.orig, eyetracking.window2.summary.by.trial.orig, eyetracking.window3.summary.by.trial.orig, eyetracking.window.summary.by.trial) %>% 
   filter(time.window != "end", time.window != "pre-verb-onset", condition != "filler" ) %>% 
  group_by(study, condition, time.window, subject) %>% 
  summarize(mean_prop = mean(prop.fixations.animal, na.rm = T)) %>% 
  mutate(time.window = factor(time.window, 
                            levels = c("post-verb-onset-pre-animal-onset",
                                       "post-animal-onset-pre-instrument-onset",
                                       "post-instrument-onset"),
                            labels = c('Verb to animal \n("Rub the")',
                                       'Animal onset\n("frog with the")',
                                       'Instrument+1500ms\n(feather...")')),
         condition  = factor(condition, 
                             levels = c("modifier", "equibiased", "instrument"), 
                             labels = c("Modifier", "Equi-biased", "Instrument"))
         ) %>% 
  ungroup()

eyetracking.window.summary.both = eyetracking.window.summary.by.subj.both %>% 
  group_by(study, condition, time.window) %>% 
  summarize(mean_prop = mean(mean_prop, na.rm = T), 
            se_prop = sd(mean_prop, na.rm = T)/sqrt(n()))

```{r E4-proportion-fix-by-window-both, fig.cap = "Proportion of target fixations by verb bias in the original dataset (Ryskin et al., 2017) and the current data collected online. Error bars reflect bootstrapped 95% CIs over subject means"}

ggplot(eyetracking.window.summary.by.subj.both)+
  stat_summary(aes(x=time.window, color=condition, y = mean_prop, shape = study), 
               geom = 'point', fun = 'mean', size = 3)+
 stat_summary(aes(x=as.numeric(time.window), y = mean_prop, linetype = study, group=paste(condition, study) ),
             geom = 'line', fun = 'mean', alpha = 0.5, color = "grey")+
  stat_summary(aes(x=as.numeric(time.window), y = mean_prop, color = condition, group = paste(condition , study)), 
                geom = 'errorbar', fun.data = 'mean_cl_boot', width = 0.05)+
  #facet_wrap(~time.window)+
  scale_color_brewer(palette = "Set1")+
  scale_shape_manual(values = c(1,16))+
  scale_linetype_manual(values = c("dashed","solid"))+
  coord_cartesian(ylim = c(0,.8))+
  theme_classic()+
  labs(y = "Proportion of fixations", x = NULL)
```
```{r, eval  = F}
orig.data.time.window.1 <- eyetracking.window1.summary.by.trial.orig %>% 
  filter(condition != "filler") %>% 
  mutate(condition = fct_drop(condition))
contrasts(orig.data.time.window.1$condition) <- cbind(c(-2/3, 1/3, 1/3), c(0, -1/2, 1/2))

@@

```{r, eval  = F}
orig.data.time.window.2 <- eyetracking.window2.summary.by.trial.orig %>% 
  filter(condition != "filler") %>% 
  mutate(condition = fct_drop(condition))
contrasts(orig.data.time.window.2$condition) <- cbind(c(-2/3, 1/3, 1/3), c(0, -1/2, 1/2))

@@

```{r, eval  = F}
orig.data.time.window.3 <- eyetracking.window3.summary.by.trial.orig %>% 
  filter(condition != "filler") %>% 
  mutate(condition = fct_drop(condition))
contrasts(orig.data.time.window.3$condition) <- cbind(c(-2/3, 1/3, 1/3), c(0, -1/2, 1/2))

model.time.window.3 <- lmer(prop.fixations.animal ~ condition + (1 | subject) + (1 | trialID), data=orig.data.time.window.3 )
summary(model.time.window.3)
```
